An assessment of photometric redshift PDF performance in the context of LSST

### 2018-11-13 paper/tex/analysis.tex
address all but one comment in 4.1 and 4.2

The probability integral transform (PIT) \citep{Polsterer:16} is defined for each individual galaxy as:%essentially the derivative of the QQ plot, a histogram of

@@

The CDE loss is defined as:
\begin{equation} \label{eq:cde-loss}
L(f, \widehat{f}) = \int \int (f(z \mid \x) - \widehat{f}(z \mid \x))^{2} dz dP(\x)
\end{equation}
This loss is the CDE equivalent of the RMSE in regression. To estimate this loss we rewrite the loss as
\begin{equation} \label{eq:estimated-cde-loss}
\mathbb{E}_\X \left[\int \widehat{f}(z \mid \X)^{2} dz\right] - 2 \mathbb{E}_{\X,Z}\left[\widehat{f}(Z \mid \X)\right] + K_{f},
\end{equation}
where the first expectation is with respect to the marginal distribution of the covariates $\X$, the second expectation is with respect to the joint distribution of $\X$ and $Z$, and $K_{f}$ is a constant depending only upon the true conditional densities $f(z\mid \x)$.
For each method we can estimate these expectations as empirical expectations on the test or validation data \citep[Eq.~7 in][]{Izbicki:17b} without knowledge of the true densities.

@@

\begin{equation}
\mathrm{RMSE} = \sqrt{\int_{-\infty}^{\infty}\left(\hat{f}(z)-f'(z)\right)^{2}\,dz},
\end{equation}
%may be used for two purposes in this analysis.
%We calculate it between the true redshift distribution $N'(z)$ and each estimator $\hat{N}(z)$ (derived by Eq.~\ref{eq:stacked}) as well as between the ideal QQ and PIT curves from each method studied and the ideal curves.
Though this metric does not account for the fact that the redshift distribution function is, in fact, a probability distribution, it can still be interpreted as a measure of the integrated difference between the estimated distribution and the true distribution, and it can be used to quantify the otherwise qualitative metrics.

@@

The \textit{Kolmogorov-Smirnov statistic} $N_{\rm KS}$ is the maximum difference between $F_{\rm phot}(z)$ and $F_{\rm spec}(z)$, the CDFs of the photo-$z$ and spectroscopic redshift respectively:

\begin{equation}
N_{\rm KS} = \max_{z}\left( \left| F_{\rm phot}(z) - F_{\rm spec}(z) \right| \right).
\end{equation}
%The KS test quantifies whether the two redshift distributions are drawn from a similar distribution, independent of binning.
The KS test quantifies the similarity between two distributions, independent of binning.
A lower $N_{\rm KS}$ value corresponds to more similar distributions.
%We calculate two KS test statistics, one to test the distribution of $p(z)$ values, and one to test the stacked estimator $\hat{n}(z)$ of the redshift distribution.
%The $p(z)$ test compares the CDF of the PIT values described in the previous section to that of a uniform distribution.
%The $n(z)$ test compares the CDF of the distribution formed by stacking the $p(z)$ for every object in our test set against the CDF of the corresponding true redshifts.
%In this case a lower $N_{\rm KS}$ value means that the photo-$z$ distribution fits the spectroscopic redshift distribution well. $F_{\rm phot}(z)$ is calculated by stacking the PDFs of every single object in the sample, producing a smooth cumulative $n(z)$ to be compared with $F_{\rm spec}(z)$.

@@

\begin{equation}
\label{eq:cvm}
\omega^2 = \int_{-\infty}^{+\infty}\big(F_{\mathrm{meas.}}(x) - F_{\mathrm{ideal}}(x)\big)^2\mathrm{d}F_{\mathrm{ideal}}
\end{equation}
% In this paper we use the CvM statistic to evaluate the performance of both $n(z)$ and $p(z)$.
The AD statistic is a weighted version of the CvM statistic, making it more sensitive to the tails of the distribution:

>>>>

The probability integral transform (PIT) has been employed recently to evaluate fidelity of posterior distributions  \citep[e.~g.~][]{Bordoloi:10,Polsterer:16,Tanaka:17}.  The PIT value is defined for each individual galaxy as:%essentially the derivative of the QQ plot, a histogram of

@@

The CDE loss is defined as:
\begin{equation} \label{eq:cde-loss}
L(f, \widehat{f}) = \int \int (f(z \mid \x) - \widehat{f}(z \mid \x))^{2} dz dP(\x)
\end{equation}
This loss is the CDE equivalent of the RMSE in regression. To estimate this loss we rewrite the loss as
\begin{equation} \label{eq:estimated-cde-loss}
L(f, \widehat{f}) = \mathbb{E}_\X \left[\int \widehat{f}(z \mid \X)^{2} dz\right] - 2 \mathbb{E}_{\X,Z}\left[\widehat{f}(Z \mid \X)\right] + K_{f},
\end{equation}
where the first expectation is with respect to the marginal distribution of the covariates $\X$, the second expectation is with respect to the joint distribution of $\X$ and $Z$, and $K_{f}$ is a constant depending only upon the true conditional densities $f(z\mid \x)$.
For each method we can estimate these expectations as empirical expectations on the test or validation data \citep[Eq.~7 in][]{Izbicki:17b} without knowledge of the true densities.

@@

\begin{equation}
\mathrm{RMSE} = \sqrt{\int_{-\infty}^{\infty}\left(\hat{f}(z)-f'(z)\right)^{2}\,dz},
\end{equation}
%may be used for two purposes in this analysis.
%We calculate it between the true redshift distribution $N'(z)$ and each estimator $\hat{N}(z)$ (derived by Eq.~\ref{eq:stacked}) as well as between the ideal QQ and PIT curves from each method studied and the ideal curves.
Though this metric does not account for the fact that the redshift distribution function is, in fact, a probability distribution, it can still be interpreted as a measure of the integrated difference between the estimated distribution and the true distribution.%, and it can be used to quantify the otherwise qualitative metrics.

@@

The \textit{Kolmogorov-Smirnov statistic} $N_{\rm KS}$ is the maximum difference between $F_{\rm phot}(z)$ and $F_{\rm true}(z)$, the CDFs of the photo-$z$ and true redshift distributions respectively:

\begin{equation}
N_{\rm KS} = \max_{z}\left( \left| F_{\rm phot}(z) - F_{\rm true}(z) \right| \right).
\end{equation}
%The KS test quantifies whether the two redshift distributions are drawn from a similar distribution, independent of binning.
The KS test quantifies the similarity between two distributions, independent of binning.
A lower $N_{\rm KS}$ value corresponds to more similar distributions.
%We calculate two KS test statistics, one to test the distribution of $p(z)$ values, and one to test the stacked estimator $\hat{n}(z)$ of the redshift distribution.
%The $p(z)$ test compares the CDF of the PIT values described in the previous section to that of a uniform distribution.
%The $n(z)$ test compares the CDF of the distribution formed by stacking the $p(z)$ for every object in our test set against the CDF of the corresponding true redshifts.
%In this case a lower $N_{\rm KS}$ value means that the photo-$z$ distribution fits the spectroscopic redshift distribution well. $F_{\rm phot}(z)$ is calculated by stacking the PDFs of every single object in the sample, producing a smooth cumulative $n(z)$ to be compared with $F_{\rm spec}(z)$.

@@

\begin{equation}
\label{eq:cvm}
\omega^2 = \int_{-\infty}^{+\infty}\big(F_{\mathrm{meas.}}(x) - F_{\mathrm{ideal}}(x)\big)^2\mathrm{d}F_{\mathrm{ideal}}
\end{equation}
% In this paper we use the CvM statistic to evaluate the performance of both $n(z)$ and $p(z)$.
While the KS statistic is a good measure near the median of a distribution, the AD statistic, a weighted version of the CvM statistic, is much more sensitive to the tails of the distribution, providing complementary information:
